SPORES: Transferring files as spores through the wind instead of up in the Cloud

### 2019-06-12 short-talk/contents.tex
Improves short talk slides

\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Alice and Bob have privacy against each other.
      \item Someone Else can see everything.
    \end{itemize}
  \end{remark}

@@

  \begin{question}
    \begin{itemize}
      \item Can we remove Someone Else's central position?
      \item And still have privacy?
    \end{itemize}
  \end{question}
\end{frame}

@@

\begin{frame}
  \begin{idea}
    \begin{itemize}
      \item We leverage that each user have multiple devices.
      \item Some subset of devices is online at any given time.
      \item Alice and Bob will use Carol's and David's devices for relaying.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}
  \begin{center}
    \includegraphics[height=0.5\textheight]{fig/principle-SPOR.png}
  \end{center}

  \begin{block}{Approach}
    \begin{itemize}
      \item We adapt the Sphinx mix-header format.
      \item Still universally composable.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \begin{example}[Scenario]
    \begin{itemize}
      \item Alice wants to send a file to Bob.
      \item \emph{Bob} encodes a SPOR route as a URL and sends to Alice.
      \item Alice \enquote{wraps} a route around Bob's.
      \item She sends the file over the route.
    \end{itemize}
  \end{example}

>>>>

\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Alice and Bob enjoy privacy against each other.
      \item Someone Else can see everything.
    \end{itemize}
  \end{remark}

@@

  \begin{question}
    \begin{itemize}
      \item Can we remove Someone Else's central position?
      \item And still enjoy privacy?
    \end{itemize}
  \end{question}
\end{frame}

@@

\begin{frame}
%  \begin{idea}
%    \begin{itemize}
%      \item We leverage that each user have multiple devices.
%      \item Some subset of devices is online at any given time.
%      \item Alice and Bob will use Carol's and David's devices for relaying.
%    \end{itemize}
%  \end{idea}

  \begin{center}
    \includegraphics[height=0.6\textheight]{spores-squads.png}
  \end{center}
\end{frame}

@@

\begin{frame}
  \begin{center}
    \includegraphics[height=0.25\textheight]{sphinx-route.png}
  \end{center}

  \begin{center}
    \includegraphics[height=0.4\textheight]{sphinxes-route.png}
  \end{center}
\end{frame}

\begin{frame}
  \begin{example}[Scenario]
    \begin{itemize}
      \item Alice wants to send a file to Bob.
      \item \emph{Bob} encodes a route as a URL and sends to Alice.
      \item Alice \enquote{wraps} a route around Bob's.
      \item She sends the file (chunks) over the route.
    \end{itemize}
  \end{example}
